---
title: 'Week 8: Ordinary Least Squares (OLS) Regression'
output: html_document
runtime: shiny
editor_options: 
  markdown: 
    wrap: 72
---

> In this notebook we will learn to code bivariate and multivariate
> regression and interpret the results.

## OLS (bivariate) regression

Ordinary Least Squares (OLS) regression is a method for assessing a
linear relationship between an independent variable ğ‘‹ and a dependent
(outcome) variable $Y$. Our equation for the regression model looks like
this: \$\$Y_i = \hat{\alpha} + \\hat{\\beta} X_i + \\hat{u}\_{i}\$\$Here
$(X_i, Y_i)$ represent a sample data point. (There are $n$ values of ğ‘–,
where $n$ is the sample size.) ğ›¼Ì‚ and ğ›½Ì‚ represent the Y-intercept and the
slope of the regression line, respectively. $\hat{u}_i$ represents a
sample residual (or error). We can see this visually by using a modified
version of a function we used to understand correlations in model 7. The
code below reproduces the figure we saw in the last module but also
includes the regression line and a graphical representation of the
residual for each point in the dataset. Note that the residual (error),
the vertical distance between our data points and the regression line,
is bigger for some data points than for others.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
```

```{r correlate, echo = FALSE}

simcor = function (correlation, n = 50, min = 0, maxi = 1, ymean = 0, ysd = 1) {
    x=runif(n = n, min = min, max = maxi)
    ymean = ymean
    ysd = ysd
    y = rnorm(n) 
    z = correlation * scale(x)[,1] + sqrt(1 - correlation^2) * scale(resid(lm(y ~ x)))[,1] 
    y_new = ymean + ysd * z 
    plot(x,y_new, ylab = "Y values", xlab = "X values", main = "Errors and Regression Line")
    abline(lm(y_new~x))
    pre <- predict(lm(y_new~x))
    segments(x, y_new, x, pre, col="red") 
}

inputPanel(
    sliderInput("corr", label = "Correlation Coefficient:",
              min = -1, max = 1, value = .7, step = 0.05),
    selectInput("n", label = "Number of Points:", 
                choices = c(10, 25, 50, 100, 200), selected = 50),
)

renderPlot(simcor(input$corr, input$n))
```
